### 2013-09-23 pystruct/paper.tex
copyedit nyu, be clear about improving upon the state of the art on msrc.
starting blabla on superpixels and CRFS

\section{Casting Structured Prediction into Software}\label{sec:api}

@@

We demonstrate the use of \pystruct on the task of semantic image segmentation,
the main focus of this work. The example shows how to learn an $n$-slack support
vector machine on a superpixel-based CRF on the popular Pascal dataset. We use
unary potentials generated using TextonBoost
from \citet{krahenbuhl2012efficient}. The superpixels are generated using SLIC~\citep{achanta2012slic}.%
\footnote{The preprocessed data can be found at \url{http://www.ais.uni-bonn.de/download/datasets.html}.}
Each sample (corresponding on one entry of the list \texttt{X}) is represented as a
tuple consisting of input features and a graph representation.
\begin{listing}[t]
\begin{pythoncode}
model = crfs.EdgeFeatureGraphCRF(
            class_weight=inverse_frequency,
            symmetric_edge_features=[0, 1],
            antisymmetric_edge_features=[2],
            inference_method='qpbo')

>>>>

\section{Casting Structured Prediction into Software}\label{sec:pystruct}

@@

We demonstrate the use of \pystruct on the task of semantic image segmentation,
the main focus of this work. The example shows how to learn an $n$-slack support
vector machine on a superpixel-based CRF on the popular Pascal dataset. Details of the experiment
can be found in Chapter~\ref{exact_learning}.
Each sample (corresponding on one entry of the list \texttt{X}) is represented as a
tuple consisting of input features and a graph representation.
\begin{listing}[t]
\begin{pythoncode}
model = crfs.EdgeFeatureGraphCRF(
            class_weight=inverse_frequency,
            symmetric_edge_features=[0, 1],
            antisymmetric_edge_features=[2],
            inference_method='qpbo')

### 2013-09-23 structured_prediction/paper.tex
starting blabla on superpixels and CRFS

>>>>

\section{CRFs for Semantic Segmentation}
Conditional Random Fields have been established as an important tool in many
areas of computer vision. Applications include dense stereo, optical flow, 
inpainting, de-noising, image editing, low-level segmentation and semantic segmentation.

There are broadly two types of models that are used: models in which each pixel
in an image is represented as a node, and models in which pixels are first
grouped together into superpixels and each superpixel is represented as a node.
In pixel-based CRFs edges are usually introduced between adjacent pixels, that is using
either 4-neighborhoods or 8-neighborhoods. Superpixel-based approaches introduce
edges between adjacent superpixels, that is those that share a boundary.
%TODO images of superpixels!
%
The motivation for using superpixels is that it is often easy to group nearby
pixels that belong to the same object just based on local color or texture cues.
While it is hard to even define what makes a sensible segmentation of an image,
it is much easier to define, and also to compute an \emph{over-segmentation}.
The only requirement for an over-segmentation is that each segment only
contains pixels belonging to the same entity.

Using superpixels instead of pixels has large computational advantages.
A model that uses superpixels contains much fewer variables than one that works on pixel-level.
Typical sizes for superpixels are in the hundereds of pixels, leading to a hundred-fold decrease
in complexity for prediction. There are also semantic advantages. Using superpixels
can constitute a form of regularization, including prior knowledge about the structure
of images. Modeling interactions between superpixels also allows more distant parts of an image
to interact, instead of modeling long-term relations only indirectly over neighbors.
Finally, modeling decisions on a superpixel-level allows for more context for a local decision,
while semantic decisions on pixel-level are not meaningful near object boundaries.
The main disadvantage of superpixel-based approaches is that the initial oversegmentation can
not be influenced by later reasoning. This can be a problem if fine structures need to be
segmented for which local evidence does not suffice.

% about algorithms, slic?
% hierarchical\dots has superpixels and pixels?
%  pro/con superpixels?

% submodular/non-submodular? higher order?

In early models, parameters were usually set by hand. Recent works mostly use a
maximum margin based formulation based on maximum margin Markov
models~\cite{taskar2003max} or structural ssvms~\cite{tsochantaridis2006large}
for parameter learning~\cite{lucchi2013learning, lucchi2011spatial}.

Most CRF-based image segmentation approaches use loopy neighborhood graphs,
leading to intractable inference problems during learning -- see
\citep{nowozin2010parameter} for a tree based approach. There has been much
research in learning structured prediction models using approximate inference.
The influence of approximate inference on structured support vector machine
training was first analyzed in  \citep{finley2008training}.

More recently, \cite{meshi2010learning}, \cite{hazan2010primal} and
\cite{komodakis2011efficient} introduced formulations for joint inference and
learning using duality.

\citep{finley2008training} shows that using certain Linear Programming (LP)
relaxations, generalization guarantees can be preserved. Unfortunately,
standard LP solvers are too slow for many applications, in particular semantic
segmentation as formulated in this work.

Most related to our approach is \citep{szummer2008learning}, which utilize graph cut
based optimization for inference.
Instead of using the classical approach of \cite{boykov2001fast}, which is restricted
to submodular potentials, we use a $\alpha$-expansion move-making algorithm based on binary QPBO
\cite{rother2007optimizing}. While relying on local search loses the guarantees of binary QPBO,
this method is fast and we find it to perform well in practice.
